Sizing the bets in a focused portfolio

### 2024-02-11 doc/paper.tex

\noindent The software is freely available at TODO. Reader is referred to its
documentation for instructions on how to install and use the software.

>>>>

\noindent The software is freely available as a Rust crate
at~\url{https://crates.io/crates/charlie}, and its source code is hosted on
GitLab at~\url{https://gitlab.com/in-silico-public/charlie}. The reader is
referred to its documentation for instructions on how to install and use the
software.
